---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lenght

<!-- badges: start -->
[![R-CMD-check](https://github.com/cobrbra/lenght/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cobrbra/lenght/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of lenght is to provide convenient aliases for each of the common misspellings of the R function `length`, a problem that haunts us all.

## Installation

You can install the development version of lenght from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cobrbra/lenght")
```

## Example

You can use the functions in `lenght` to do anything the base R function `length` would do.

```{r example}
library(lenght)
print(lenght(1:4))

print(lentgh(options()))

print(lenhgt(NULL))
```

## Contact 

Feel free to leave issues or pull requests on our GitHub [repository](https://github.com/cobrbra/lenght), or alternately to contact the package maintainer Jacob by [email](mailto:cobrbradley@gmail.com).
